\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

\vspace{24pt}
\namesection{\bf Dhivya}{G.}{
\urlstyle{same}
\href{mailto:gdhivya.0810@gmail.com}{\texttt{\textbf{gdhivya.0810@gmail.com}}} |
\textbf{\textbf{$+91 8939379935$}} |
\href{https://www.linkedin.com/in/dhivya-g-1403a128a}{linkedin.com/in/dhivya-g}
}

\begin{minipage}[t]{0.45\textwidth} 

\section{\textbf{Profile}}
\vspace{2pt}

\textbf{Highly motivated} Computer Science and Engineering student at \textbf{SRM IST}, passionate about \textbf{AI}, \textbf{Machine Learning}, and \textbf{Data Science}. Skilled in programming, data analysis, and model development, with a focus on \textbf{deep learning}, \textbf{NLP}, and \textbf{computer vision}. Strong \textbf{analytical}, \textbf{problem-solving}, and \textbf{communication skills}, thriving in collaborative environments. Open to learning, adapting, and exploring new opportunities!

%====================
% EDUCATION
%====================
\vspace{4pt}

\section{Education}
\vspace{2pt}
\subsection{SRMIST, Ramapuram}
\vspace{4pt}
\location{B.Tech in Computer Science \\ and Engineering - 2026}
\location{\bf CGPA: 7.4}
\vspace{12pt}
\subsection{ST. URSULA'S ANGLO-INDIAN HIGHER SECONDARY
SCHOOL PRESENTATION CONVENT, CHURCH PARK}
\location{HSC - 2020}
\location{\bf PERCENTAGE: 86\%}

\vspace{4pt}

\section{Skills}
\vspace{2pt} 
\subsection{Domains}
\vspace{4pt}
Full-Stack Development, Machine Learning , Data science\\
\vspace{8pt}
\subsection{Languages}
\vspace{4pt}
Advanced: C, Python, HTML,CSS\\
Intermediate: c++, java script\\

\vspace{6pt}
\subsection{Others}
\vspace{4pt}
AWS, GitHub\\
\vspace{6pt}
\subsection{Soft Skills}
\vspace{4pt}
Problem solving, Communication, Leadership



\vspace{4pt}

\section{Certifications}
\vspace{4pt}
\descript{Python For Data Science}
\location{NPTEL | Jan – Mar 2025}
\vspace{4pt}
\descript{Introduction to ML}
\location{NPTEL | Jul – Nov 2024}
\vspace{4pt}
\descript{JavaScript with HTML}
\location{SRM AXIS Intellects | Jul – Dec 2023}
\vspace{2pt}

\section{Workshops \& Outreach}
\vspace{2pt}
\descript{Artificial Intelligence Workshop}
\location{IIT Madras | 2025}
\vspace{4pt}
\descript{Community Connect}
\location{Chennai Lions Eye Bank Trust \& RIO-GOH |}
\textbf{{Jun – Jul 2024}
}

\end{minipage} 
\hfill
\begin{minipage}[t]{0.49\textwidth} 

\section*{\textbf{Experience}}
\vspace{2pt}

\subsection{8Queens Software Technologies Pvt Ltd} \\ 
\textit{Full-Stack Development Intern}

\textit{Feb 2025 – Mar 2025 | Chennai, India} \\
\begin{itemize}
  \item Built and optimized landing pages using HTML, CSS, and JS for client projects.
  \item \textbf{Tech Stack:} HTML, CSS, JavaScript, Node.js, React
\end{itemize}

\vspace{2pt}

\subsection{PLASMID} \\
\textit{Machine Learning Intern}

\textit{Dec 2024 – Feb 2025} 
\begin{itemize}
  \item Built machine learning pipelines for data preprocessing and classification tasks.
  \item \textbf{Tech Stack:} Python, ML, scikit-learn, pandas
\end{itemize}


\section{Projects}

\vspace{4pt}
\runsubsection{Speech Emotion Recognition}
\descript{| ML Project}
\begin{tightemize}
\item Designed a high-precision audio classification model using Wav2Vec.
\item Tech Stack: {\bf Python, ML}
\item \href{https://github.com/Dhiv08/Speech-Emotion-Analysis-Using-Self-Supervised-Learning-using-Wav2Vec-model-for-High-Precision-Audio}{GitHub Link}
\end{tightemize}
\vspace{4pt}

\runsubsection{CropDoc}
\descript{| Early Crop Disease Detection using TensorFlow}
\begin{tightemize}
\item Developed a deep learning model to detect and classify crop diseases.
\item Tech Stack: {\bf Python, HTML, CSS, JavaScript}
\item \href{https://github.com/Dhiv08/CropDoc-HARNESSING-TENSORFLOW-FOR-EARLY-DETECTION-AND-PREDICTION-OF-CROP-DISEASES}{GitHub Link}
\end{tightemize}



\vspace{4pt}

\section*{\textbf{Achievements}}
\vspace{2pt}

\runsubsection{Academic}
\begin{itemize}
  \item Top 10 in class for consistent academic performance.
\end{itemize}

\runsubsection{Hackathons}

\begin{itemize}
  \item Awarded \textbf{Best Student of the Hackathon} by Supraja Technologies (Sep 2023).
  \item Participated in \textbf{VIT Make-a-thon}, a 24-hour hackathon event (Jan 2025).
\end{itemize}





\section{Tech Profile Links}
\vspace{4pt}
\begin{itemize}
\item \textbf{Portfolio}: \href{https://dhivyag-porfolio.netlify.app/}{\bf dhivyag-porfolio.netlify.app}
\item \textbf{LeetCode}: \href{https://leetcode.com/u/HHATnMOjx7/}{\bf Dhivya G}
\item \textbf{GitHub}: \href{https://github.com/Dhiv08}{\bf github.com/Dhiv08}
\end{itemize}


\end{minipage} 

\end{document}
